%-------------------------
% Resume in Latex
% Author : Shrinath Deshpande
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = blue %Colour of citations
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
% Main Headings like Company name with Tabular structure of Company & Place // designation & Duration
\newcommand{\resumeHeading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \vspace{-2pt}\\ \vspace{1pt}
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
      %\vspace{-5pt}
}
% Sub Headings e.g. Project Titles
\newcommand{\resumeSubheading}[1]{
      {\small\textbf{#1}} \\
      %\vspace{-5pt}
}

\newcommand{\resumeSubheadingWithDate}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \small #2 \\
    \end{tabular*}
    \vspace{+2pt}
}

\newcommand{\resumeSubheadingNew}[1]{
      {\small{#1}} \\
      %\vspace{-5pt}
}

% Reducing Gap Between Sections
\newcommand{\resumeSection}[1]{
\vspace{-12pt}
\section{\textbf{#1}}
}

% Bullet list for details
\newcommand{\resumeItemListStart}{
\vspace{-7pt}
\begin{itemize}[leftmargin=14pt]
}
\newcommand{\resumeItemListEnd}{
\vspace{+7pt}
\end{itemize}
}

\newcommand{\resumeItem}[1]{
  \item\small{
      {#1 \vspace{-7pt}
      }
  }
}

\renewcommand{\labelitemii}{$\circ$}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
 700, Health Sciences Drive, &\textbf{{\LARGE Prerna kothari}} & Email : \href{mailto:kothariprerna13@gmail.com}{kothariprerna13@gmail.com}\\
 Stony Brook, New York  &\href{https://deshpandeshrinath.github.io/}{linkedIn Link or Personal Website} & Mobile : +1-631-542-3679 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{\textbf{Education}}
    \resumeHeading
      {Stony Brook University}{Stony Brook, NY}
      {M.S. Mechanical Engineering), GPA 3.88}{Jan. 2018 -- Present}
    \resumeItemListStart
      \resumeItem{\textbf{Relevent Coursework :} Artificial Intelligence, Machine Learning, Robotics, Geometric Modeling, Product Design Optimization, Mathematics}
      \resumeItem{Developing a cloud based Machine Design Software, under the guidance of Dr. Purwar; funded by \$ 'X' NSF grant.}
    \resumeItemListEnd


%-----------EXPERIENCE-----------------
\resumeSection{Experience}
    \resumeHeading
      {Stony Brook University}{Stony Brook, NY}
      {Research Assistant}{Dec 2018 -- Present}
      \resumeItemListStart
        \resumeItem{Developing a web based platform for linkage design; A react-redux application is developed for simulating planar closed loop linkages \\ url: \href{https://prernakothari.github.io/motiongen-react/}{https://prernakothari.github.io/motiongen-react/}}
       \resumeItem{Using React-Native for cross-platform mobile version of the application.}
      \resumeItemListEnd

    \resumeHeading
      {Oracle}{Pune, India}
      {Associate Consultant}{Aug 2015 -- Dec 2017}
      \resumeItemListStart
        \resumeItem{Customization and Implementation of Banking Products in the Internet Banking and mobile-based browser domain}
       \resumeItem{Understanding banking processes and Implementation/Development to translate business needs into software.}
      \resumeItemListEnd


      \resumeSubheadingNew{\textbf{Teaching Assistant} - MEC101 (Mechanical Design Innovation), MEC 262 Engineering Dynamics}
      \resumeItemListStart
        \resumeItem{Involved in creating assignment, exams and conducting recitation sessions for 200\texttt{+} students in each course.}
      \resumeItemListEnd

%--------PROGRAMMING SKILLS------------
\resumeSection{Skills}
\vspace{+7pt}
    \resumeItemListStart
      \resumeItem{\textbf{Languages :} Proficient in Javascript, Java, Python, MATLAB, HTML5, CSS. Familiar with C\texttt{++}}
      \resumeItem{\textbf{Tools \& Technologies :} Tensorflow, React, Redux, FC@ (Flexcube Direct Banking), XSL, XML, J2EE, JBoss, EAP.}
    \resumeItemListEnd


%-----------PROJECTS-----------------
    \resumeSection{Relevant Projects}

    \resumeHeading{Deep Recurrent Attentive Writer (DRAW) VAE }{MEC 634 Machine Learning, Prof. N Chakraborty}{Tensorflow}{Jan 2018 -- May 2018}
    \resumeItemListStart
      \resumeItem{Implemented DRAW Variational Auto Encoder for Sequential Generation of Images; Neural Networks with Attention Mechanism}
      \resumeItem{Implemented in Tensorflow; Trained on MNIST, CIFAR Datasets; Reproduced the results presented in the google brain \href{https://arxiv.org/abs/1502.04623}{paper}}
    \resumeItemListEnd

    \resumeHeading{Deep Reinforcement Learning for Continuous Control Tasks}{CSE 537 AI, Prof. N Balasubramanian}{Tensorflow, OpenAI-Gym \href{https://github.com/deshpandeshrinath/deepDGP}{https://github.com/deshpandeshrinath/deepDGP}}{Jan 2018 -- May 2018}
    \resumeItemListStart
      \resumeItem{Implemented Deep DPG algorithm to learn continuous control policies; Compatible with all OpenAI-Gym environments.}
      \resumeItem{Implemented Hindsight Experience Replay for learning goal-oriented tasks with sparse binary rewards.}
    \resumeItemListEnd

    \resumeHeading{Motion Planning of Baxter Arm}{MEC529 Robotics, Prof. N. Chakraborty}{MATLAB}{March 2016 -- May 2016}
    \resumeItemListStart
      \resumeItem{Computed smooth B-Spline motion for pushing. Computed Jacobian matrix; Applied approximate Inverse Position Kinematics}
      \resumeItem{Obtained joint angles and rates for the task. Performed simulations to validate the results.}
    \resumeItemListEnd

    \resumeHeading{Interactive Manipulation of NURBS Surfaces}{MEC572 Geomtric Modelling, Prof. Anurag Purwar}{C\texttt{++}, OpenGL}{March 2016 -- May 2016}
    \resumeItemListStart
      \resumeItem{QT5, OpenGL based implementation in C\texttt{++} for interactive manipulation of Non Uniform Rational B-Spline Surfaces.}
    \resumeItemListEnd

\end{document}
