%-------------------------
% Resume in Latex
% Author : Shrinath Deshpande
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
% Main Headings like Company name with Tabular structure of Company & Place // designation & Duration
\newcommand{\resumeHeading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ %\vspace{-5pt}
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
      %\vspace{-5pt}
}
% Sub Headings e.g. Project Titles
\newcommand{\resumeSubheading}[1]{
      {\small\textbf{#1}} \\
      %\vspace{-5pt}
}

% Reducing Gap Between Sections
\newcommand{\resumeSection}[1]{
\vspace{-12pt}
\section{#1}
}

% Bullet list for details
\newcommand{\resumeItemListStart}{
\vspace{-7pt}
\begin{itemize}[leftmargin=14pt]
}
\newcommand{\resumeItemListEnd}{
\vspace{+7pt}
\end{itemize}
}

\newcommand{\resumeItem}[1]{
  \item\small{
      {#1 \vspace{-7pt}
      }
  }
}

\renewcommand{\labelitemii}{$\circ$}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://deshpandeshrinath.github.io}{\Large Shrinath Deshpande}} & Email : \href{mailto:deshpandeshrinath@gmail.com}{deshpandeshrinath@gmail.com}\\
  \href{http://github.io.deshpandeshrinath/}{http://github.io.deshpandeshrinath/} & Mobile : +1-631-633-1851 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
    \resumeHeading
      {Stony Brook University}{Stony Brook, NY}
      {Ph.D. (Major: Mechanical, Minor: Computer Science)}{Aug. 2015 -- Present}
    \resumeItemListStart
      \resumeItem{\textbf{Relevent Coursework :} Computer Vision, Machine Learning, Analysis of Algorithms, Computational Geometry, Advanced Control Systems, Robotics, Geometric Modelling for CAD, Product Design Optimization}
    \resumeItemListEnd


%-----------EXPERIENCE-----------------
\resumeSection{Experience}
    \resumeHeading
      {Stony Brook University}{Stony Brook, NY}
      {Research Assistant, Teaching Assistant}{May 2016 -- Present, Aug 2015 -- May 2016}
      \resumeSubheading{Machine Learning}
      \resumeItemListStart
        \resumeItem{Research on machine learning techniques for kinematic synthesis of planar mechanisms.}
        \resumeItem{Performed dimensionality reduction using Auto-Encoders.}
        \resumeItem{Developed a data driven approach to mechanism synthesis.}
      \resumeItemListEnd

      \vspace{-5pt}
      \resumeSubheading{Optimization}
      \resumeItemListStart
          \resumeItem{Developed an optimization routine for planar four-bar linkage synthesis.}
          \resumeItem{Led to award winning publication for solving practical synthesis problems (doi: 10.1115/1.4037801)}
      \resumeItemListEnd

      \vspace{-5pt}
      \resumeSubheading{MotionGen: Website, iOs and Android App for Linkage Synthesis}
      \resumeItemListStart
          \resumeItem{Developed core modules of a cross platform App for planar mechanism synthesis and simulation.}
          \resumeItem{Written in Javascript, HTML, CSS and built with Apache Cordova framework.}
      \resumeItemListEnd

      \vspace{-5pt}
      \resumeSubheading{Teaching Assistant - Design Innovation, Engineering Dynamics}
      \resumeItemListStart
        \resumeItem{The undergraduate courses at Stony Brook University, had more than 200 students per course enrolled.}
        \resumeItem{Involved in creating assignment, exams and conducting recitation sessions.}
      \resumeItemListEnd
%-----------PROJECTS-----------------
\resumeSection{Relevant Projects}
    \resumeHeading{Visual Odometry}{CSE527 Computer Vision, Prof. Roy Shilkrot} {Python, Tensorflow, OpenCV}{Oct 2017 -- Dec 2017}
    \resumeItemListStart
      \resumeItem{End-to-end Monocular Visual Odometry using deep Recurrent Convolutional Neural Networks.}
      \resumeItem{Trained and tested on KITTI odometry dataset.}
      \resumeItem{Implemented in Tensorflow and OpenCV.}
    \resumeItemListEnd

    \resumeHeading{Unsupervised Machine Learning}{CAD Innovation and Engineering Lab, Stony Brook}{Python, Javascript, Tensorflow, Scikit-Learn} {Sep 2017 -- Dec 2017}
    \resumeItemListStart
      \resumeItem{Developed a data driven approach to motion synthesis.}
      \resumeItem{Performed dimensionality reduction using Autoencoder Neural Networks.}
      \resumeItem{Resulted in quick and efficient motion queries for mechanism synthesis.}
    \resumeItemListEnd

    \resumeHeading{MotionGen}{CAD Innovation and Engineering Lab, Stony Brook}{Apache Cordova framework (JS, HTML, CSS)}{Dec 2015 -- June 2017}
    \resumeItemListStart
      \resumeItem{A cross platform App for planar mechanism synthesis and simulation.}
      \resumeItem{Implemented several modules including Tolerance Based Synthesis, B-Spline Curve Generation.}
      \resumeItem{Worked with open source Apache Cordova framework for iOs and Android implementations.}
    \resumeItemListEnd

    \resumeHeading{Central Trajectory Problem}{CSE555 Computational Geometry, Prof. Joseph Mitchell}{CGAL, OpenGL, Boost, C\texttt{++}}{March 2017 -- May 2017}
    \resumeItemListStart
      \resumeItem{Developed an algorithm for finding valid representative trajectory among n time stamped trajectories.}
      \resumeItem{Algorithm based on dijkstra's shortest path. Implemented in C++ using CGAL, OpenGL, Boost libraries}
    \resumeItemListEnd

    \resumeHeading{Optimal Control of a Drifting Car}{MEC560 Advanced Control Systems, Prof. Vivek Yadav}{GPOPS-II, MATLAB}{Oct 2016 -- Dec 2016}
    \resumeItemListStart
      \resumeItem{Performed planning and optimal control of a car in drifting conditions using GPOPS-II.}
      \resumeItem{MATLAB based implementation available at deshpandeshrinath.github.io}
    \resumeItemListEnd

    \resumeHeading{Motion Planning of a Serial Manipulator}{MEC529 Robotics, Prof. N. Chakraborty}{MATLAB}{March 2016 -- May 2016}
    \resumeItemListStart
      \resumeItem{MATLAB based implementation of Trajectory Planning and Inverse Kinematics of Baxter Arm for Planar Pushing Task.}
    \resumeItemListEnd

   % \resumeHeading{Interactive Manipulation of NURBS Surfaces}{MEC572 Geomtric Modelling, Prof. Anurag Purwar}{C\texttt{++}, OpenGL}{March 2016 -- May 2016}
   % \resumeItemListStart
   %   \resumeItem{QT5, OpenGL based implementation in C\texttt{++} for interactive manipulation of Non Uniform Rational B-Spline Surfaces.}
   % \resumeItemListEnd

%--------PROGRAMMING SKILLS------------
\resumeSection{Skills}
\vspace{+7pt}
    \resumeItemListStart
      \resumeItem{\textbf{Languages :} Proficient in Python, Javascript, MATLAB. Familiar with C\texttt{++}, HTML, CSS}
      \resumeItem{\textbf{Technologies :} Experienced with Git, Tensorflow, OpenCV, Numpy, Scikit-learn, Unix/Linux, Boost, STL, Apache Cordova}
    \resumeItemListEnd
%-------------------------------------------

\resumeSection{Awards}
    \resumeSubheading{A.T. Yang Award in Theoretical Kinematics (Aug 2017)}
    \resumeItemListStart
      \resumeItem{Awarded \$1000 for the Best Paper at ASME Mechanisms and Robotics Conference, Cleveland, OH, August, 2017}
    \resumeItemListEnd
\end{document}
